Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-20 paper_comparison/paper_comparison/paper_comparison.tex
captions on Effect size

Figure \ref{fig:poly-example} shows one of the ten lineups where the
visual test rejected the residual plot. The data plot, in position three
is very obvious, and different from the nulls. The visual test was
correct to reject. To understand why this is, one needs to return to the
way the RESET test is applied. It requires a parameter indicating degree
of polynomial to test for, and the recommendation is to generically use
4 (XXX REF). However, the ``M'' and the ``Triple-U'' shapes constructed
from the Hermite polynomials use power up to 6 and 18 respectively. All
10 lineups rejected by the visual test but not the RESET were of types
``M'' or ``Triple-U''. If the RESET test had been applied using the
power up to 6, all the decisions for these lineups would have been to
reject. The recommendation of the polynomial power for the RESET should
be revised, perhaps. This illustrates the sensitivity of conventional
testing to the parameters, and it also points to a limitation that one
needs to know the data structure in order to set the parameters for the
test.

@@

\caption{Power of conventional tests and visual tests on lineups produced by the non-linearity model under different distributions of regressor.}\label{fig:different-x-dist-poly-power}
\end{figure}

>>>>

Figure \ref{fig:poly-example} shows one of the ten lineups where the
visual test rejected the residual plot. The data plot, in position
three, is very obvious, and different from the nulls. The visual test
was correct to reject. To understand why this is, one needs to return to
the way the RESET test is applied. It requires a parameter indicating
degree of polynomial to test for, and the recommendation is to
generically use 4 (XXX REF). However, the ``M'' and the ``Triple-U''
shapes constructed from the Hermite polynomials use power up to 6 and 18
respectively. All 10 lineups rejected by the visual test but not the
RESET were of types ``M'' or ``Triple-U''. If the RESET test had been
applied using the power up to 6, all the decisions for these lineups
would have been to reject. The recommendation of the polynomial power
for the RESET should be revised, perhaps. This illustrates the
sensitivity of conventional testing to the parameters, and it also
points to a limitation that one needs to know the data structure in
order to set the parameters for the test.

@@

\caption{Power of conventional tests and visual tests on lineups produced by the non-linearity model under different fitted value distributions.}\label{fig:different-x-dist-poly-power}
\end{figure}
